---
title: "Syllabus"
format: 
  html: default
---

```{r setup, message = FALSE, warning = FALSE, include = FALSE}
library(tidyverse)

library(tinytable)

knitr::opts_chunk$set(fig.align = 'center')
```

:::: {.grid .course-details .course-details-smaller}

::: {.g-col-12 .g-col-sm-6 .g-col-md-4}
<!--
   .g-col-12: grid span 12 columns (full width) on extra-small screens
   .g-col-sm-6: grid span 6 columns (half width) on small screens
   .g-col-md-4: grid span 4 columns (1/3 width) on medium+ screens 
-->

### Instructor

- [{{< fa user >}}]{.fa-li} {{< var instructor.name >}}
- [{{< fa university >}}]{.fa-li} {{< var instructor.office >}}
- [{{< fa envelope >}}]{.fa-li} <a href='mailto:{{< var instructor.email >}}'>{{< var instructor.email >}}</a>
:::

::: {.g-col-12 .g-col-sm-6 .g-col-md-4}
### Course Details

- [{{< fa calendar-days >}}]{.fa-li} {{< var course.days >}}
- [{{< fa clock >}}]{.fa-li} Section A: {{< var course.timeA >}}
- [{{< fa clock >}}]{.fa-li} Section B: {{< var course.timeB >}}
- [{{< fa location-dot >}}]{.fa-li} {{< var course.location >}}
:::

::: {.g-col-12 .g-col-sm-6 .g-col-md-4}
### Office Hours

- [{{< fa calendar-check >}}]{.fa-li} {{< var office_hours >}} or by appointment
:::

::::

## Textbook

This website is a companion to the course pack you purchased from the bookstore.

## Technology

Any scientific calculator

## Course Prerequisite

We live in a world in in which data drives decision making. Data is everywhere! The purpose of this course is to provide a comprehensive overview of the statistical literacy required to cope with the practical demands of daily life in a way that encourages responsible citizenship in modern democracy. Course objectives will emphasize critical thinking and problem solving, with the application of statistical skills to real-world scenarios requiring reasoning from evidence. Overall, this course is an introduction to the fundamental concepts and methods of statistics. Topics include data organization; graphs and numerical measures; probability; normal, and sampling distributions; confidence intervals and hypothesis testing; correlation; and regression.

## CORE Literacy - Quantitative Reasoning 

Quantitative reasoning may be thought of as one’s ability to not only apply traditional algorithms to solve problems, but to also understand why such algorithms are appropriate and use them to make decisions, justifications, and reflections in a variety of real-world situations. Modern democracy requires citizens to be adept at applying quantitative information to make sound judgements and inferences that promote thoughtful stewardship. 

## CORE Value - Thoughtful Stewardship 

We are dedicated to stewardship: to the care of each other, to the preservation of our historical buildings and natural resources, to the responsible management of our financial resources and gifts, and to the celebration of the remarkable heritage of St. Augustine with its vibrant cultures and history.

## Student Learning Outcomes and Competencies 

Upon completion of the quantitative reasoning requirement, student will be able to

  - Analyze, interpret, and communicate information through a written statistical report.
  - Use algebraic techniques to solve problems and express relations.
  - Analyze and interpret descriptive and inferential statistics appropriately to describe a given data set.
  - Identify and use appropriate technology/software in problem solving and decision making.
  - Calculate and evaluate the appropriateness of statistical measures of central tendency and variability based on real-world context and the shape of the data distribution.
  - Analyze and interpret rational number data presented in various ways (e.g., stem-and-leaf plots, box plots, line plots, histograms, tables, bar graphs, circle graphs).
  - Identify and interpret numerical and categorical data presented in various forms (e.g., histograms, circle graphs, scatterplots, two-way tables) to solve problems.
  - Analyze and evaluate how the presentation of data (e.g., scaling, chosen form) or selection of statistics (e.g., mean, median, mode) can lead to different or inappropriate interpretations in real-world contexts.
  - Calculate and interpret the meaning of measures of central tendency (mean, median, mode) and variability (range, standard deviation) in real-world or abstract contexts from numerical and categorical data sets.

## Course Requirements and Methods of Assessment 

  - Participation -- Students are required to be active participants in and out of the classroom. In-class assignments and daily notes checks contribute to this grade. Additionally, small assignments in preparation for the course project will be counted in this category. **Every missing set of completed notes, even when absent, will result in a 5% drop to this category.**
  - Quizzes -- Four online quizzes in Canvas
  - Unit Exams -- Four 50-minute in-class unit exams
  - Final Exam -- A 2-hour comprehensive final exam will be given .
  - Final Project -- A group project will be completed during the last unit of study. Students will be given data to analyze through descriptive and influential statistical methods. We will work on different portions of the project throughout the semester.

## Course Grade Weighting

  - Participation: 10%
  - Quizzes: 10%
  - Unit Exams: 50%
  - Final Exam: 20%
  - Final Project: 10%

## Late Work Policy

_No late project, exams, or quizzes are accepted. Participation assignments may be submitted *with instructor's approval* in the case of absence._

## Method of Instruction 

The primary mode of delivery will be lectures. 

## Attendance Policy 

It is essential in the pursuit of academic excellence in all Mathematics and Technology courses that students attend class regularly. Students are, therefore, expected to attend class as part of their personal responsibility toward this pursuit of excellence. Missing more than 20% of class time (8 classes) may result in your instructor withdrawing you from class with either a "W" or "WF," depending upon the timing published for course withdrawals by the Registrar. **Please stay home if you are sick. You do not need to contact your instructor unless it happens to be on a test date.**

If a student is absent on the date of a test, the absence must be an unavoidable excused absence (documented illness or emergency) in order for the test to be made up. **If you have a documented unavoidable excused absence on the date of a test, you MUST notify the professor within 24 hours of the test session to schedule a make-up, or you will receive a zero for the test, regardless of the reason for the absence. Note that planned absences for events are not considered excused and tests must be taken in advance of any planned absences.**

**It is not permissible to leave class early or arrive tardy. You are expected to remain in the classroom throughout the duration of the class meeting.** Your instructor may consider you absent for any disruptions to the class, including tardiness, early departures, and evictions from the class for disrupting others. 

## Artificial Intelligence Policy 

Generative AI is a powerful tool that has its uses in certain contexts, but it is not appropriate for the learning goals in this course. In statistics, we rely on skills such as analytical thinking and evidence-based decision-making that are developed through practice and improvement. As a result, you will be given opportunities to practice and grow without the use of AI. Use of Generative AI for the completion of assignments or activities will be considered academic dishonesty in the context of this course and will result in zeros on applicable assignments and/or referral to the Dean of Academic Life for further consequences.

## Learning Resource Center 

The Flagler College Math lab is located in the Learning Resource Center. Please visit the Learning Resource Center’s website [www.flagler.edu/LRC](www.flagler.edu/LRC) to check the times, schedule an appointment, and get detailed information.

## General Expectations 

  +	Students are expected to bring their course notebook and a calculator to all class meetings.
  +	Students are expected to participate in the class discussion/activity.
  +	Students are expected to spend a minimum of six hours per week outside of class on course preparation. This includes reading and outlining the textbook, reviewing class notes, doing the required homework and quizzes, and working on the final project.
  +	Students are expected to communicate with their instructor using Canvas and/or official Flagler College email for all electronic communication. Email communication should be used in a professional manner by using proper email etiquette and including an informative subject line. Please allow up to 24 hours for a response.
  +	Students must check all Canvas Announcements and their Flagler College email daily.
  +	Students must set up their StatCrunch account using their Flagler College email. 

## Grading Scale

```{r grading-scale, include = FALSE}
grading <- tribble(
  ~Grade, ~Range,  ~Grade1, ~Range1,
  "A",  "93–100%", "C",  "73–76%",
  "A−", "90–92%",  "C−", "70–72%",
  "B+", "87–89%",  "D+", "67–69%",
  "B",  "83–86%",  "D",  "60–66%",
  "B−", "80–82%",  "F",  "< 60%",
  "C+", "77–79%",  "", "" 
)
```

::: {.centered-table}

```{r show-grades-table, echo=FALSE}
grading |>
  setNames(c("Grade", "Range", "Grade", "Range")) |> 
  tt() |> 
  style_tt(line = "b", line_width = 0.05, line_color = "#d3d8dc") |> 
  style_tt(i = 1, line = "t", line_width = 0.1, line_color = "#d3d8dc") |> 
  style_tt(j = 2, bootstrap_css = "border-right: 0.1em dashed #d3d8dc;")
```

:::